---
title: "BH-TEDS Visualization Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{BH-TEDS Visualization Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include=FALSE, message=TRUE, warning=TRUE}
# Reference: https://bookdown.dongzhuoer.com/hadley/r-pkgs/vignettes.html
# Reference: https://r-pkgs.org/vignettes.html#vignette-workflow-2

library(ggplot2) # Plots. 
library(dplyr) # Data manipulation. 
library(magrittr) # Pipe operator. 
library(gridExtra) # Arrange plots + tables. 
library(stringr) # For str_wrap() function. 
library(forcats) # For fct_relable() function.

source("../R/bhteds_helper_functions.R")

# theme_set(theme_bw(base_size = 8)) # plot theme. 

knitr::opts_chunk$set( # Set defaults for knit-to-output. 
  error = FALSE,     # display error message and keep going if there is an error when set to TRUE.
  tidy = FALSE,      # Display code as typed if set to FALSE, otherwise reformat if set to TRUE.
  size = "small",    # Slightly smaller font for code.
  fig.width = 6.0,   # Width of figures (can be overridden in individual chunks).
  fig.height = 4.0,  # Height of figures (can be overridden in individual chunks).
  fig.show = "asis", # Put all figures after all the code.
  results = "asis",  # Don't wrap text output in verbatim code blocks, but leave asis. 
  collapse = FALSE,   # Output immediately follows code. 
  
  echo = TRUE,      # Always show R code (this is the default).
  eval = TRUE,      # Always evaluate code chunks. 
  include = TRUE,   # Similar to echo and eval, but if FALSE, will still evaluate code but won't show R code.
  message = TRUE,  # enable/disable messages.
  warning = TRUE   # enable/disable warnings.
)
```

===========================================================================================================  

```{r}
bhteds_data <- readRDS("bhteds_data.RDS")
bhteds_data_labels <- readRDS("bhteds_data_labels.RDS")
```

===========================================================================================================  

#### Generate Plots + Tables:  

Choose county (and reference county(ies)) to filter by.  
```{r}
unique(bhteds_data$county)
```

Choose variable(s) to generate aggregate statistics for.  
```{r}
colnames(bhteds_data)
```

Specify variables to use and associate variable names with their preferred labels.  
```{r}
my_vars <- c(
  "inttx", "srvset", "prevtrmt", "psacode", "ssacode", "tsacode", "opioid", "anyopioid", "daystx2", "ageyr10", "adultchild", 
  "gender", "gendid", "pregnant", "minwag", "race", "ethnic", "educatGrp", "mrtlstat", "empstat", "income2", "veteran", 
  "livargmt", "corrstat")

bhteds_data_labels <- bhteds_data_labels %>% 
  mutate(variable = row.names(bhteds_data_labels)) 

var_lab_list <- list()
for(i in 1:nrow(bhteds_data_labels)) {
  var_lab_list[bhteds_data_labels[i, 2]] <- bhteds_data_labels[i, 1]
}
# Create labels for variables without one (or modify them). 
var_lab_list["anyopioid"] <- "Medication Assisted Opioid Treatment (any opioid)"
var_lab_list["daystx2"] <- "Days to Treatment Group"
var_lab_list["ageyr10"] <- "Age Group"
var_lab_list["adultchild"] <- "Adult/Child"
var_lab_list["educatGrp"] <- "Education"
var_lab_list["income2"] <- "Income Group"
```

===========================================================================================================  

Call function.  
```{r, warning=TRUE, message=TRUE}
# Reference: https://rstats-tips.net/2020/07/31/get-rid-of-info-of-dplyr-when-grouping-summarise-regrouping-output-by-species-override-with-groups-argument/  
options(dplyr.summarise.inform = FALSE)

my_filters <- list()
# my_filters[["gender"]] <- c("==", "Female")
# my_filters[["ageyears"]] <- c(">", "20")

start_time <- Sys.time()

results <- visualize_bhteds_demographics(
  data = bhteds_data, 
  labels_data = var_lab_list, 
  county_filter = "Allegan", 
  ref_county_filter = c("Barry", "Oakland"), 
  subset_filter = my_filters, 
  fiscal_year = "FY2022 Q1-Q3", 
  stats_vars = my_vars, 
  ref_stat_type = "median")

end_time <- Sys.time()
```

Returned objects from function.  
```{r}
names(results)
end_time - start_time
```

===========================================================================================================  

Post-hoc adjustments to plots/tables (function returns list of ggplot plot objects and dataframes for tables)  
```{r, fig.width=12, fig.height=12}
plot2 <- results[["srvset plot"]] + scale_x_discrete(labels = function(x) str_wrap(x, width = 12))

table2 <- gridExtra::tableGrob(results[["srvset table"]], 
                               theme = bhteds_grid_table_theme(table = results[["srvset table"]]))
gridExtra::grid.arrange(plot2, table2)
```

